### 2018-03-23 Sections/multi_packet_operations.tex
minor

Thus far we have considered nodes which implement single-packet operations. However, many real-world quantum protocols (to be presented in Sec.~\ref{sec:protocols_quant_int}) will require multi-packet operations, which must be carefully combined in some well-defined way. For example, for state teleportation (Sec.~\ref{sec:teleport}) we must combine a data packet with half of a Bell pair (Sec.~\ref{sec:bell_state_res}). For entanglement swapping (Sec.~\ref{sec:swapping}) -- the essential component in quantum repeater networks (Sec.~\ref{sec:rep_net}) -- two halves of distinct Bell pairs undergo a joint entangling measurement.

>>>>

Thus far we have considered nodes which implement single-packet operations. However, many real-world quantum protocols (to be presented in Sec.~\ref{sec:protocols_quant_int}) will require multi-packet operations, which must be carefully combined in some well-defined way. For example, for state teleportation (Sec.~\ref{sec:teleport}) we must combine a data packet with half of a Bell-pair (Sec.~\ref{sec:bell_state_res}). For entanglement swapping (Sec.~\ref{sec:swapping}) -- the essential component in quantum repeater networks (Sec.~\ref{sec:rep_net}) -- two halves of distinct Bell-pairs undergo a joint entangling measurement.

### 2018-03-23 Sections/physical_architectures_for_quantum_computing.tex
minor

To analyse the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single qubit clusters, which we assume `come for free'\footnote{As in beer.\index{Beer}}). For example, the second element of the vector tells us how many 3-qubit linear clusters we have in our possession.

@@

Alternately, if there is no direct line of quantum communication between two qubits, an EO can be performed by directly employing the same idea in reverse. We imagine that a third party, such as a satellite, acts as a server for entangled Bell pairs. Two parties receive one qubit each from the pair. Then they perform an EO between their halves of the Bell pair and their local qubits. With appropriate local corrections, mediated by only cheap classical communication, this teleports the action of an EO onto the two qubits, creating a link between them.

>>>>

To analyse the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single-qubit clusters, which we assume `come for free'\footnote{As in beer.\index{Beer}}). For example, the second element of the vector tells us how many 3-qubit linear clusters we have in our possession.

@@

Alternately, if there is no direct line of quantum communication between two qubits, an EO can be performed by directly employing the same idea in reverse. We imagine that a third party, such as a satellite, acts as a server for entangled Bell-pairs. Two parties receive one qubit each from the pair. Then they perform an EO between their halves of the Bell-pair and their local qubits. With appropriate local corrections, mediated by only cheap classical communication, this teleports the action of an EO onto the two qubits, creating a link between them.

### 2018-03-23 Sections/protocols_for_the_quantum_internet.tex
minor

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SuperdenseCoding($\ket{B_{00}}$, $x$):
\begin{enumerate}
\item Alice and Bob share the Bell pair $\ket{B_{00}}$.
\item Alice encodes the two-bit string \mbox{$x\in\{0,1\}^2$} into a choice of the four possible Bell pairs.
\item Alice prepares the respective Bell pair using operations local to only her half of the shared state ($\hat{\mathbb{I}}$, $\hat{X}$, $\hat{Z}$ or \mbox{$\hat{Z}\hat{X}$}).
\item Alice sends her qubit to Bob.
\item Bob measures in the Bell basis, with four possible measurement outcomes.
\item The measurement outcome corresponds to the bit-string $x$.
\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{x_0} & \cw & \cw & \control \cw \\
\lstick{x_1} & \cw & \control \cw \\
\lstick{} & \qw & \gate{X} \cwx & \gate{Z} \cwx[-2] & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \rstick{x_0} \\
\lstick{} & \qw & \qw & \qw & \qw & \ghost{\text{Bell}} & \cw & \rstick{x_1}
\inputgroupv{3}{4}{.8em}{.8em}{\ket{B_{00}}\quad} \\
} \nonumber
\end{align}
}}}
\caption{Superdense coding protocol for communicating two classical bits via transmission of a single qubit. The protocol requires the two parties share a Bell-pair as a resource, provided by a third party.} \label{alg:superdense}
\end{table}

@@

There are however several outstanding problems with the quantum clock synchronisation scheme as presented above. In the scheme of Jozsa \textit{et al.}, if one starts in a perfect singlet state\index{Singlet state}, the scheme works as intended, but if one instead starts with the state, 
\begin{align}
\frac{1}{\sqrt{2}} ( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B ),
\end{align}
(a Bell pair augmented by a local phase) one obtains an offset to the synchronisations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions chosen by the two parties. Thus, in practice entanglement purification\index{Entanglement purification} would be required to produce a singlet state with \mbox{$\delta=0$} prior to executing the protocol. However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronised clocks \cite{bib:preskill2000quantum} --  this renders syncrhonisation impossible. It has previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification\index{Entanglement purification} \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs\index{Singlet state} are shared.

>>>>

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SuperdenseCoding($\ket{B_{00}}$, $x$):
\begin{enumerate}
\item Alice and Bob share the Bell-pair $\ket{B_{00}}$.
\item Alice encodes the two-bit string \mbox{$x\in\{0,1\}^2$} into a choice of the four possible Bell-pairs.
\item Alice prepares the respective Bell-pair using operations local to only her half of the shared state ($\hat{\mathbb{I}}$, $\hat{X}$, $\hat{Z}$ or \mbox{$\hat{Z}\hat{X}$}).
\item Alice sends her qubit to Bob.
\item Bob measures in the Bell basis, with four possible measurement outcomes.
\item The measurement outcome corresponds to the bit-string $x$.
\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{x_0} & \cw & \cw & \control \cw \\
\lstick{x_1} & \cw & \control \cw \\
\lstick{} & \qw & \gate{X} \cwx & \gate{Z} \cwx[-2] & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \rstick{x_0} \\
\lstick{} & \qw & \qw & \qw & \qw & \ghost{\text{Bell}} & \cw & \rstick{x_1}
\inputgroupv{3}{4}{.8em}{.8em}{\ket{B_{00}}\quad} \\
} \nonumber
\end{align}
}}}
\caption{Superdense coding protocol for communicating two classical bits via transmission of a single qubit. The protocol requires the two parties share a Bell-pair as a resource, provided by a third party.} \label{alg:superdense}
\end{table}

@@

There are however several outstanding problems with the quantum clock synchronisation scheme as presented above. In the scheme of Jozsa \textit{et al.}, if one starts in a perfect singlet state\index{Singlet state}, the scheme works as intended, but if one instead starts with the state, 
\begin{align}
\frac{1}{\sqrt{2}} ( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B ),
\end{align}
(a Bell-pair augmented by a local phase) one obtains an offset to the synchronisations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions chosen by the two parties. Thus, in practice entanglement purification\index{Entanglement purification} would be required to produce a singlet state with \mbox{$\delta=0$} prior to executing the protocol. However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronised clocks \cite{bib:preskill2000quantum} --  this renders syncrhonisation impossible. It has previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification\index{Entanglement purification} \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs\index{Singlet state} are shared.
